---
title: "README"
author: "Yves Deville"
date: "2023-05-22"
output: github_document
---


# The bever package

The **bever** package is a R package funded by IRSN/Behrig. 

This package is devoted to some Bayesian approaches in Extreme Value
(EV) modelling, with focus on Markov Chain Monte-Carlo. The package
does not implement by itself the Bayesian estimation or inference of
any EV model. These tasks are left to the **revdbayes** package or to
some other MCMC sampler as can be implemented by using **JAGS** or
**Stan**. The **bever** package aims at producing some classical
results or plots such as Return Level tables or plots. Its goal is to
allow a comparison of the frequentist and Bayesian inference methods
when applied to EV models.

The name **bever** relates to **B**ayes **E**xtreme-**V**alue. In some
modern or ancient European languages, the word relates to the *river*
or/and to one of its famous inhabitant. Hydrology may be one field of
application.


## Important notes

This package is still in its early stage of development

- The use of block maxima with block duration differing from 1 is
  not well tested.

- For now it is possible to draw the predictive curve on the same
  graphics as the RL plot only for GEV models, not for Poisson-GP
  models. The reason is that some analysis is still required for the
  transformation of plotting positions in "Renext style" tu use them
  in "block style".


# INSTALLATION

## Using the *remotes* package

In an R session use

```{r, eval=FALSE}
library(remotes)
install_github("IRSN/bever", dependencies = TRUE, auth_token = myToken)
```

where `myToken` is *your* GitHub token. This should install the
package and make it ready to use.

Mind that by default this does not build the vignette shipped with the
package (long-form documentation). To build the vignette, use instead

```{r, eval=FALSE}
install_github("IRSN/bever", dependencies = TRUE, auth_token = myToken, build_vignettes = TRUE)
```
The installation will then take a longer time but the vignette will be
accessible from the help of the package (link above the "Help Pages"
section).

You can also select a specific branch or a specific commit by using
the suitable syntax for `install_github`. For instance to install the
branch `develop` use

```{r, eval=FALSE}
install_github("IRSN/bever@develop", dependencies = TRUE)
```
See the **remotes** package documentation for more details.

## Clone, build and install

### Cloning the repository

You can also clone the repository to install the package.  If you do
not have yet a local `bever` repository, use `git clone` to clone the
`bever` repository

``` bash
git clone https://github.com/IRSN/bever
```

This will create a `bever` sub-directory of the current directory,
i.e. the directory from which the git command was issued. Of course
this can work only if you have the authorisation to clone.

### Installation

Move to the parent directory of your cloned repository and use the
following command from a terminal to create a tarball source file

``` bash
R CMD build bever
```
This will produce a source tarball `bever_x.y.z` where `x`, `y` and
`z` stand for the major, minor and patch version numbers. Then you can
install from a command line

``` bash
R CMD INSTALL bever_x.y.z
```
Note that you must also have all the packages required by **bever**
installed.

You can also use the **RStudio** IDE to install the package.
