---
title: "bever Package: User's Guide"
author: "Yves Deville"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Goals and Uses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: bever.bib
---

```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
    cache = FALSE,
    fig.width = 6, fig.height = 4, fig.path = "Rgraphics/")
KABLE <- TRUE
library(bever)
library(ismev)
```

		      
This document was created with **bever**
**`r packageVersion("bever")`** and **potomax**
**`r packageVersion("potomax")`**.  As is the case for the whole package,
this vignette is to be considered as a DRAFT version that still needs,
checking, renaming, ...

# Introduction

## Goals

The package **bever** is devoted to Extreme-Value models considered
from the Bayesian perspective. It depends on the **potomax** package
which consider the same models from a frequentist perspective with
emphasis on the Maximum-Likelihood (ML) approach. So the two
perspectives can be compared by using the same data and by producing
similar results such as the classical Return-Level plots. So **bever**
aims at producing these graphics and diagnostics. Although the package
contains some functions dedicated to the estimation and inference of
these Bayesian models, the results can also be produced by using
Markov Chain Monte-Carlo with different R packages or even by using a
sampling engine such as **JAGS** or **stan**.  **bever** will
then essentially retain the MCMC iterates.
     
## Extreme-Value Models
	
The package focuses on four types of Extreme-Value models,
conveniently represented by an acronym (or abbreviated names) as
follows.
   
1. `"GEV"` **GEV model** or Block Maxima. The parameters are: $\mu^\star$
   (location), $\sigma^\star$ (scale) and $\xi^\star$ (shape). The
   blocks are assumed to have a constant known duration.

2. `"OS"` models for **$r$-largest order statistics** in blocks. The
   parameters are the GEV parameters $\mu^\star$, $\sigma^\star$,
   $\xi^\star$ as for block maxima, in reference with a constant block
   duration.

3. `"PP"` **Point-Process model** for Peaks Over Threshold (POT). The
   parameters are GEV parameters $\mu^\star$, $\sigma^\star$,
   $\xi^\star$ for a reference block duration. This model is fitted by
   using observations exceeding a given high threshold $u$.  The
   parameters do not depend on $u$ and the support of the distribution
   includes values that are $<u$.
   
	     
4. `"poisGP"` **Poisson-GP model** for POT. This model describes
   observations exceeding a given high threshold $u$. The parameters
   are: the rate $\lambda$ for the Poisson process of exceedances and
   the two parameters: $\sigma$ (scale) and $\xi$ (shape) for the
   Generalised Pareto (GP) distribution of the excesses over the given
   threshold.

In a first stage at least, the functions and methods are devoted in
priority to the `"GEV"` and `"poisGP"` models.

The acronyms as used with the package will be case-insensitive, so
`"pp"` and `"PP"` can be indifferently used for the Point-Process
model of 3. So the model types are consistent with **revbayes**,
although `"poisGP"` is not (yet) implemented in this package which
uses instead the the binomial-GP model `"binGP"`.

Speaking of "models" as we did is somewhat abusive because the
Point-Process or Poisson-GP models lead to the GEV block maxima model
when they are aggregated in time, while the Block-Maxima or the Order
Statistics models do not fully describe the extreme observations
occurring within the blocks. These two later models do not provide a
data generation process. We will consider the `"GEV"` and `"OS"`
models as derived from a Poisson-GP process, either in its `"PP"` or
in its `"poisGP"` parameterisation.  Indeed, we could consider `"GEV"`
and "`OS"` models as resulting form a temporal aggregation from a POT
model as implemented in the `Renouv` function of **Renext**. As a
major difference between `"PP"` and `"poisGP"`, the parameters of
`"poisGP"` relate to the threshold $u$, while those of `"PP"` do not.
Of course, while the `"PP"` parameter vector $[\mu^\star,
\sigma^\star, \xi^\star]$ do not depend on the threshold $u$, its
estimate $[\widehat{\mu}^\star, \widehat{\sigma}^\star,
\widehat{\xi}^\star]$ does depend on $u$ which controls the censoring
of the observations. However it is that the estimate remains quite
stable when the threshold is high enough and when there remains enough
data.
   
The models above will in this vignette be considered both from a
frequentist and from a Bayesian perspective. In the second case, the
inference will generally be based on Markov Chain Monte-Carlo (MCMC).
    
## Fitted models as S3 classes

### Classical "fitted model" objects
	   
Following a vague terminology making sense at least for R users, we
may call *fitted models* the results of estimation and inference for a
specific couple *model* and *data*. The archetype would be the
(fitted) linear model with the `"lm"` S3 class. A very common way to
use a specific type of model in R consists in first creating an object
by using the corresponding *constructor function*, to which the data
are passed as formal argument(s). Then S3 methods such as `plot`,
`summary`, `coef` are used. The name of constructor function is often
chosen identical to the name of the S3 class: an object with class
`"lm"` is created by using the `lm` function.


### "Poor Man's" Posteriors
	       
While these "gentleman's rules" are retained in the package, we will
in some cases allow the user to create fitted models objects by using
results arising from other packages, as opposed to the usual fitting
from data. For Bayesian fitted models, we will allow to create these
from MCMC iterates as produced by other packages, possibly relying on
sampling engines such as **JAGS** or **stan**. Doing so, the user is
responsible for keeping track of the specific data that were used,
these being no longer automatically duplicated into the fitted model
object. However for each of the models defined above, there is a
*minimal set of information* which must be given to allow the use of
the model e.g. to derive predictions. Depending on the type of model,
this involves: the *block duration*, the *observation duration* and
possibly the *threshold*. The following table tells if an information
is needed (Y) or not (N) depending on the type of object created.
   
| Model    | Block duration |     Obs. duration    | Threshold |
|:---------|:--------------:|:--------------------:|:---------:|
|`GEV`|Yes|(# blocks)|No|    
|`OS`|Yes|(# blocks)|No|
|`poisGP`|No|Yes|Yes|
|`PP`|Yes|Yes|Yes|

We can call an objects created from MCMC iterates *minimalist* or
*poor man*'s posteriors. As shown later, they actually contain very
little more than what can be guessed from the matrix given in `MCMC`.

While a fitted model should in principle embed a copy of all the
information used for the fit - including the data, this assumption is
likely to be over-demanding as far as we are interested in by-products
such as graphics or diagnostics. So the creator functions for "poor
man's posteriors" will use several optional arguments.

The current version focuses on *only two EV models*: GEV and Poisson-GP,
and provides the following objects             
            
| Model    | Bayes from data | Bayes from MCMC|
|:---------|:---------:|:--------:|
|GEV| |`GEVBayes0`|    
|Poisson-GP|`poisGPBayes`|`poisGPBayes0`|

So the convention is (for now) that "from MCMC" objects have names
ending by `0` to suggest an impoverishment relative to the classical object.
Note for the GEV model only the "from MCMC" option is available.
	
### Illustration: GEV model for `portpirie`
   
Consider first fitting a GEV model for the `portpirie` data from **revdbayes**.
We define a prior that can be used with the `"gev"` model
	  	
```{r PoorMan_GEV1, message=FALSE}  
priorGEV1 <- set_prior(prior = "flatflat", model = "gev")
postGEV1 <- rpost_rcpp(n = 10000, model = "gev", prior = priorGEV1, data = portpirie)
class(postGEV1)
head(postGEV1$sim_vals, n = 3)
```

The MCMC iterates are stored in the `sim_vals` element of the
posterior object.  Using *this information only*, we can create a Poor
Man's Posterior.
	
```{r PoorMan_GEV2, message=FALSE} 
postGEV0 <- GEVBayes0(MCMC = postGEV1$sim_vals)
class(postGEV0)
```
	
So the object `postGEV0` inherits from a class named `"Bayes0"`
containing minimalist Bayesian objects. As its names suggests, the
sub-class `GEVBayes0` is devoted to GEV models.
	
```{r PoorMan_GEV3, message=FALSE} 
summary(postGEV0)
coef(postGEV0)
vcov(postGEV0)
```

Note that the parameters have been renamed: while **revdbayes** uses
`mu`, `sigma` and `xi`, the corresponding parameters are now named: `loc`,
`scale` and `shape` which better conforms to older EV packages.	Note also
that the block duration was by default considered as begin `1.0`.

The `coef` method can be used to extract estimates of the
parameters. Several estimates can be computed from the `MCMC` matrix
given: posterior mean, median of mode (MAP). The posterior mode was
not displayed here nor computed because it is better to compute it by
maximising the posterior function, but this function can not be
retrieved from the MCMC iterates. The `GEVBayes0` function has a `MAP`
formal argument that can be used to pass the MAP vector when
available. This MAP will then be stored in the `GEVBayes0` object and
it can later be used e.g. to build RL plots.

It should be noted that by using "MAP", we generally name the *joint
mode* and not the *vector of marginal modes*.  By contrast, the median
in `coef` is a vector of *marginal* medians, and not a multivariate
median. For the mean there is no difference between *joint* an
*marginal*.

$$
\color{red}{\text{XXX Maybe change something in the package about Bayes
		      coef?}}
$$	     

   
We could call an object such as `postGEV0` a *minimalist* or *poor
man* s posterior. It actually contains very little more than what can
be guessed from the matrix given in `MCMC`.


### Illustration: Poisson-GP model for the `rainfall` data

The creation of a Poor Man's Posterior for a Poisson-GP model is a bit
more tedious, mainly because this model is not very popular in the
existing packages and especially not in **revdbayes** which favours the
Binomial-GP model. Assuming that the rate $\lambda$ and the GP
parameter $[\sigma,\, \xi]$ are a priori independent, these will
remain a posteriori independent as long as ordinary data only are
used.

We begin by retrieving  the GP part of the posterior
    
```{r PoorMan_poisGP_1, message=FALSE}
data(rainfall)
rainfall2 <- rainfall[!is.na(rainfall)]
u <- 40  ## threshold (mm)
w <- 57  ## obs duration (year)
nOT <- sum(rainfall2 > u)
nSim <- 10000
priorGP1 <- set_prior(prior = "flatflat", model = "gp")
postGP1 <- rpost_rcpp(n = nSim, model = "gp", prior = priorGP1,
                      data = rainfall2, thresh = u)
class(postGP1)
head(postGP1$sim_vals, n = 3)
```

To get MCMC iterates for the rate $\lambda$ of the Poisson process of
exceedances, we simply assume that a conjugate gamma prior is used,
resulting in a gamma posterior from which we can easily simulate.
   	
	
```{r PoorMan_poisGP_2, message=FALSE}
MCMCpoisGP <- cbind(lambda = rgamma(nSim, shape = 1 + nOT, rate = 0 + w),
                    postGP1$sim_vals)
postGP0 <- poisGPBayes0(MCMC = MCMCpoisGP, threshold = u, effDuration = w) 
summary(postGP0)
coef(postGP0)
```

Since the difficult part of the posterior is the "GP" part, the
`poisGPBayes0` function allows the use of a MCMC argument corresponding to a
matrix with only two columns corresponding to the MCMC iterates for the
GP parameter. In this case we have to provide the number of exceedances
by using the `nOT` format argument, because this number is needed to
determine the (gamma) posterior.

```{r PoorMan_poisGP_3, message=FALSE}
postGP0b <- poisGPBayes0(MCMC = postGP1$sim_vals, threshold = u,
                         effDuration = w, nOT = nOT) 
summary(postGP0b)
coef(postGP0b)
```
Note that the estimates for the GP part are *exactly* the same as
before because they are based on the same MCMC iterates, while the
estimate for the rate are slightly different because they no longer
rely on MCMC iterates but rather on the *exact* marginal posterior for
$\lambda$.


### Note on Poor Man's Posteriors `*Bayes0`
   
Remind that the parameters of the EV models considered in **bever**
relate to the GEV distribution, except for the Poisson-GP model for
which $\sigma$ and $\xi$ are the scale and the shape parameter of the
Generalised Pareto Distribution.

In this package, we use the convention that the parameters of the GPD
and GEV distributions are named : `"loc"`, `"scale"` and
`"shape"`. This conforms to the rule used in **Renext** and in
classical EV packages such as **evd**, **ismev** or **extRemes**. The
rate of the Poisson process in the Poisson-GP model is named
`"lambda"`. Again, this conforms to the rule used in **Renext**.

Since the **bever** package aims at "importing" MCMC iterates from
other R packages or software tools, it strives to understand several
naming rules. For instance the parameter names used by **revdbayes**
will be automatically translated into the names retained above. We
believe that this strategy is unlikely to result into a
misinterpretation of the parameters: it seems unlikely that a GEV
shape parameter could be named `"sigma"` or `"mu"`. In case of doubt, the
user will have to rename the columns of her MCMC matrices.

**CAUTION** For now no extensive tests have been made to asses a
possible change of the order of the parameters.
    
# Bayes frameworks: priors and posteriors

The models or parameterisations described above can be used in a Bayesian
framework. Here are some details.

## Poisson-GP framework

For the Poisson-GP model, some priors can be regarded as favourable.
We will consider the prior based on the two following assumptions

- The rate $\lambda$ and the GP parameter $[\sigma, \, \xi]$ are a
  priori independent.

- The rate is a priori Gamma with shape $a_0>0$ and rate $b_0 \geqslant 0$.  

The case $b_0= 0$ corresponds to an improper prior $\pi(\lambda)
\propto \lambda^{a_0-1}$ which can make sense at least for $0 < a_0
\leqslant 1$. The special case $a_0 = 1$ corresponds to constant prior
density for $\lambda$ i.e. to an improper uniform distribution on the
support $(0,\,\infty[$.
  
*Inasmuch only ordinary "OT" observations are used*, the posterior
is characterised by the following two properties.

- The rate $\lambda$ and the GP parameter
  $\boldsymbol{\theta}_{\text{GP}} := [\sigma, \, \xi]$ are a posteriori
  independent.

- The rate is a priori Gamma with shape $a_n = a_0 +n$ and rate $b_n =
  b_0 + w$ where $n$ is the number of exceedances and $w$ is the
  duration of the observation period.

However it should be kept in mind that the assumptions on the prior
are relative to the threshold $u$: if these assumptions hold for a
threshold $u$, they no longer hold for a threshold $u' > u$. Since the
threshold $u$ is generally not known and has to be chosen empirically,
the assumptions on the prior should be regarded as a trick to reach
some computing simplifications and not as a theoretically well-founded
rule.

## Other frameworks

For the other frameworks `GEV`, `rLOS` and `PP` the priors are for the
vector $[\mu^\star,\,\sigma^\star,\,\xi^\star]$ of GEV parameters in
relation with a specific block duration $w_{\text{block}}$, usually
taken as one year. Some specific priors are available in the
**revdbayes** package.

     
# Return level plots
     
## Classical Return Level plots: frequentist or Bayesian

### Displayed elements
       
This plot uses a time period $T$ as abscissa and a quantile as
ordinate. The shown elements can be as follows.

- A point estimate of the return level $\rho(T)$ for a running
period $T$ can be displayed as a curve. In the frequentist framework,
the *ML estimate* $\widehat{\rho}(T)$ will usually be shown. In the
Bayesian framework, the *mode* (MAP), the *median* and the *mean* of
the posterior distribution for $\rho(T)$ can be used.

- The uncertainty on the estimates are can be shown by using confidence
intervals on $\rho(T)$ in the frequentist framework, or credible
intervals on $\rho(T)$ in the Bayesian framework.

- Finally we can display the observations used in the fit as "sample"
points. This involves the use of suitable *plotting positions*.

When using **bever**, this plot will be obtained by first calling
the `RL` method, then the `autoplot` method on the result which was
produced by `RL`. The `autoplot` method produces a ggplot graphics
object that can be modified. The three graphical elements above
described correspond to layers of the `ggplot` object.

### Illustration for Poisson-GP fitted models
   
Consider first a frequentist fit using Garonne data from **Renext**.
Since we aim at profile-likelihood inference on the return levels
rather than the delta method, we will use the `protomax::poisGP`
function to fit a frequentist Poisson-GP model

```{r GaronneML, message=FALSE}
library(bever)
y <- Garonne$OTdata$Flow
u <- Garonne$OTinfo$threshold
w <- Garonne$OTinfo$effDuration
gfitML <- poisGP(data = y, threshold = u, effDuration = w)
class(gfitML)
coef(gfitML)
confint(gfitML)
autoplot(gfitML) +
    ggtitle("Fitted Poisson-GP model for \"Garonne\"") + theme_gray()

```
The `autoplot` S3 method produces a RL plot as a **ggplot2**
graphics. The method used here is for the class `"poisGP"`. Note that
it is easy to add or overwrite annotations, labels, ...
	
The RL plot is similar to the one that would be obtained with
**Renext** but the confidence intervals are here obtained by
profile-likelihood and not by the delta method. These intervals are
usually asymmetric, and the Upper bound is usually larger than
that obtained by the delta method.
	
The `RL` method can be used to compute the return levels frm an object
with class "`poisGP`". This method then returns an object inheriting
from the `"data.frame"` class which can again be used with `autoplot`.
    
```{r GaronneML_RL1, message=FALSE}
gRLML <- RL(gfitML, confintMethod = "proflik", trace = 0)
class(gRLML)
tail(gRLML, n = 6)
autoplot(gRLML) +
    ggtitle("Classical RL plot : frequentist POT for Garonne") + theme_gray()

```

Now let use compare our frequentist results to those obtained with a
Bayesian analysis of the same data
	
```{r GaronneBayes_RL2, message=FALSE}
gfitBayes <- poisGPBayes(data = y, threshold = u, effDuration = w)
class(gfitBayes)
coef(gfitBayes)
```

By default the Poisson parameter $\lambda$ and the GP parameter
$[\sigma, \, \xi]$ are assumed a priori independent and both have a
vague prior: the flat gamma prior for $\lambda$ and the `"flatflat"`
prior of **revdbayes** is used for the GP parameter. The posterior mode
is quite close to the ML estimate.

As for the `"poisGP"` class the `RL` method can be used for the
Bayesian objects classes `"poisGPBayes"` and `"poisGPBayes0"`
   

```{r GaronneBayes_RL3, message=FALSE}
gRLBayes <- RL(gfitBayes, trace = 0)
class(gRLBayes)
tail(gRLBayes, n = 6)
autoplot(gRLBayes) +
    ggtitle("Classical RL plot : Bayesian POT for Garonne") + theme_gray()

```

Again the Bayesian RL plot is quite close to the frequentist one: the
modal curve on the Bayesian RL is close to the quantile as estimated
by ML, and the Bayesian credible intervals on quantiles are quite
close to the profile-likelihood confidence interval for the same level
(here $70\%$), although the limits of the Bayesian intervals are lower
than those of the frequentist ones for large return periods. Of
course, the Bayesian RL plot would be different if an informative
prior had been specified.
	
Note that for the $x$-axis we use a scale which depends on the type of
model. For a `GEV` model a Gumbel scale should be used because the
theoretical RL curve corresponding to a Gumbel distribution will then
show as a straight line. For POT models either `PP` or `poisGP` a
logarithmic scale will be used because the theoretical RL curve
corresponding to an exponential distribution will show as a straight
line.

### Illustration for GEV models

We now compare the Bayesian and frequentist classical RL plots for a
GEV model. Since the Bayesian GEV model.  We use the `portpirie`
data as provided by **revdbayes**: the observations are sea levels at
Port Pirie (AU), in metres. The frequentist inference results and
return levels are described in Chap. 3 of Coles' book [@Coles_ExtremeValues].

We begin by fitting the data using ML. For that aim we can use the
`poisGP` function of the **potomax** package which can provide the
profile-likelihood confidence intervals on the return levels. Note
that since we consider block maxima the `portpirie` data must be
coerced into a list, and a vector of effective durations for the
blocks must be provided. 
	  
```{r portpirieML_RL1, message=FALSE, warning=FALSE}	   
fitp <- poisGP(MAX.data = as.list(portpirie),
               MAX.effDuration=rep(1, length(portpirie)))
autoplot(fitp) + theme_gray()
```

Since the Bayesian GEV model is available "on the shelf" in
**revdbayes**, we will use this package, and then create a minimal
posterior using `GEVBayes0` from **bever**. We reproduce here the
three lines of code that were used before.
    
```{r portpirieBayes_RL1, message=FALSE}  
prior <- set_prior(prior = "flatflat", model = "gev")
post <- rpost_rcpp(n = 10000, model = "gev", prior = prior, data = portpirie)
MAPp <- post$f_mode
names(MAPp) <- c("loc", "scale", "shape")
pfitGEV0 <- GEVBayes0(MCMC = post$sim_vals, yMax = portpirie, MAP = MAPp)
```
	
Note that the MAP must be given as a *named* vector with suitable
names.
	
Then the RL plot is obtained as follows.
	
```{r portpirieBayes_RL2, message=FALSE} 
myRL <- RL(pfitGEV0) 
autoplot(myRL) + ggtitle("Classical RL plot: Bayesian GEV for portpirie") +
    theme_gray()
```
	
The plot can be compared to the one in Figure 3.5 in Coles' book
[@Coles_ExtremeValues].
	
It can be seen that the frequentist and Bayesian results are quite
close to each other. A quite subtle difference is that the Bayesian RL
plot from **nexpot** uses a *Gumbel scale*, while that of **NSGEV**
uses an *exponential scale*. The difference is mainly on the region
corresponding to small return periods $T$, say for $T< 30$. Note that
in order to display the "sample points", we have to pass these when
creating the `GEVBayes0` object, using the `yMax` argument. We could
have created an object without giving `yMax` but it would the no
longer have been possible to show the sample points. Similarly, we could
have used the `MAP` formal argument, because the MAP is not computed by
`GEVBayes0`.

		     
## Predictive Return Level plot

### Displayed elements
	   
The plot shows the predictive distribution of the maximum $Z^\star$ to
be observed in a future or "new" period with given duration
$w^\star$. More precisely, for some values of the exceedance
probability $p$, we show the quantile $z^\star(p)$ of $Z^\star$
defined by $\text{Pr}\{Z^\star > z^\star(p)\} = p$. The duration
$w^\star$ is usually chosen to be one year, but it could be the
planned lifetime of an equipment.

An exceedance probability $p$ could be associated to the multiple
$1/p$ of $w^\star$ hence to a period - e.g. $p=0.001$ relates to the
period $1000\, w^\star$. However, in order to avoid confusions,
**bever** will not use periods as tickmarks for the $x$-axis of the
predictive RL plot.

It makes sense to display on a same plot the predictive quantile curves
corresponding to several durations $w^\star_i$. Remind that by choosing
a smaller the duration $w^\star$ we get "more conservative" quantiles,
when these are compared for a same risk $p / w^\star$. For instance a
"millennial risk" could be thought as defined by an exceedance
probability $p_1 = 0.001$ and a duration $w_1^\star = 1$ year or by
$p_2 = 0.01$ and $w_2^\star = 10$ year. In the later case we get a
smaller quantile.

	
### Illustration: Poisson-GP POT for `Garonne` data	
	
When using **bever**, this plot will be obtained by first calling
the standard `predict` method, then the `autoplot` method on the
result which was produced by `predict`. Again, the `autoplot` method
produces a ggplot graphics object that can be modified.
      
```{r gBayes_predict, message=FALSE}
gpredBayes <- predict(gfitBayes)
autoplot(gpredBayes) +
    ggtitle("Predictive RL plot : Bayesian POT for Garonne") + theme_gray()

```

### Illustration: GEV model for `portpirie`


```{r pBayes_predict, message=FALSE}
ppredGEV0 <- predict(pfitGEV0)
autoplot(ppredGEV0) +
    ggtitle("Predictive RL plot : Bayesian GEV for portpirie") + theme_gray()

```

      
We can sometimes be interested in using MCMC inference results stored
in matrix, ignoring the specific observations that were used. For
instance we can be interested in a drawing a Return-Level plot (RL
plot) from a fitted models, without caring for whether historical
information was used or not. The base ingredient to create a PMP is *a
matrix* say `MCMC` containing the MCMC iterates.

### Creating Poor Man's Posteriors

    
- Except in very special cases where the posterior contains
independent components, *the columns of `MCMC` should correspond to
the parnames of the target model*.
	    
- The *required information pieces* for the model should be given, see
above.

For instance for a GEV model, the matrix `MCMC` must have three
columns with suitable names; the block duration must be provided. The
observation duration is not required but can be given. We can further
give the observations which would allow display them on the RL plot.
     

# Relations to  other packages

## revdbayes

The **revdbayes** package uses a single S3 class to represent
posterior (or "fitted" versions) for several types of Bayesian EV
models: `gev`, `os`, `pp`, `bingp` and more. This class is named
`"evpost"`. As a difference with most classical R packages there is no
eponymous creator function, and the objects of this class are created
using either the `r_post` function or the faster-running `r_post_rcpp`
function. Both these creator functions have many formal arguments
because different types of models are allowed, depending on the value
of the formal named `model`.  An object of the class `"evpost"` is
essentially a list. Since different kinds of models can be described,
some "slots" or list elements can be `NULL`. For instance, the element
`threshold` will be `NULL` when the model is `gev` or `os`.

# XXX Questions on **bever** design

- What should return the `coef` method?

- Choose the names of the data arguments to make available the ideas
  used in **Renext**. We can fit POT models using "OT" data, "Max"
  data and "OTS" data. All three should be optional arguments of the
  `poisGPML` creator, and possibly of its Bayesian companion
  `poisGPBayes`.


# References